\newpage
\addcontentsline{toc}{section}{参考文献}
\begin{thebibliography}{0}
	
	\bibitem{System_Dynamics_Modeling}
	D. C. Karnopp, D. L. Margolis, and R. C. Rosenberg, System Dynamics Modeling and Simulation of Mechatronic Systems (Fourth Edition) [M]. New York: Wiley, 2012.
		
	\bibitem{System_Dynamics_Modeling_cn}
	D. C. Karnopp, D. L. Margolis, and R. C. Rosenberg, 黎明安（译）, 系统动力学——机电系统的建模与仿真 [M]. 国防工业出版社, 2012.
	
	\bibitem{Simulation1}
	Klee H , Allen R . Simulation of dynamic systems with MATLAB and Simulink. 2nd ed[M]// Simulation of Dynamic Systems with MATLAB and Simulink. CRC Press, Inc. 2007.
	
	\bibitem{Simulation2}
	Wouwer A V . Simulation Of ODE/PDE Models With MATLAB®, OCTAVE And SCILAB[J]. Annals of the Rheumatic Diseases, 2014, 71(Suppl 3):646-646.
	
	\bibitem{wheelchairs_review}
	Leaman, Jesse, and Hung Manh La. A comprehensive review of smart wheelchairs: past, present, and future [J]. IEEE Transactions on Human-Machine Systems 47.4 2017: 486-499.
	
	\bibitem{Bond_graph_methodology}
	Borutzky, W. Bond graph methodology, development and analysis of multidisciplinary dynamic system models (1st ed.) [M]. Berlin: Springer. 2010
	
	\bibitem{Bond_graph_modelling}
	Borutzky, Wolfgang. Bond graph modelling of engineering systems  [M]. Vol. 103. New York: Springer, 2011.
	
	\bibitem{Ayala2015ROBIO}
	Ayala, Gerardo, Rui Loureiro, and Rochdi Merzouki. Multi-domain model of steering system for an omnidirectional mobile robot  [C]. 2015 IEEE International Conference on Robotics and Biomimetics (ROBIO). IEEE, 2015.
	
	\bibitem{Sahoo2016RCTFC}
	Sahoo, Saumya Ranjan, and Shital S. Chiddarwar. Dynamic modelling of four wheel skid mobile robot by unified bond graph approach [C]. 2016 International Conference on Robotics: Current Trends and Future Challenges (RCTFC). IEEE, 2016.
	
	\bibitem{Jahanbin2016JBSMSE}
	Jahanbin, Zahra, et al. Multi-body simulation of a flapping-wing robot using an efficient dynamical model [J]. Journal of the Brazilian Society of Mechanical Sciences and Engineering 38.1 (2016): 133-149.
	
	\bibitem{Proceedings1}
	Fakri, A., Vilakazi, J. P. Modular driven wheelchair bond graph modelling [C]. The European Modeling \& Simulation Symposium, I3M2010 MultiConference, 2010, Fes, Morocco.
	
	\bibitem{Proceedings2}
	Fakri, A., Vilakazi, J. P. Wheelchair and electric drive add-on a whole bond graph modelling [C]. Proceedings of the 2014 11th International Conference on Bond graph Modeling and Simulation (ICBGM’14). SummerSim 2014 Multiconference July 6–10 2014, Monterey, CA, USA. ISBN: 978-1-63266-700-7, Vol. 46 \#8, Collection:Simulation Series, 206-210, 222 pp. 113.
	
\end{thebibliography}